Sperm should evolve to make female meiosis fair.

### 2014-05-20 writeup_and_notes/male_dependent_drive.tex
legend for fig 2 other minor rearangement

@@

\begin{figure}
\includegraphics[width = 0.8 \textwidth]{Figures/selfprom.eps}
\caption{{\bf{A.}} A visual depiction of our model of 'self-promoting' driver. 
	Transmission probabilities for alleles through female
 	 meiosis depend on sperm genotype. 
	 The non-driving $A$-allele, and self-promoting $B$-allele
	 are represented by unfilled and filled circles, respectively. 
	 {\bf{B.}} Evolution of a self-promoter and standard driver. 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	\emph{Main figure:} Boundary conditions for the invasion 
		and fixation of self-promoting and standard meiotic drivers, 
		with drive coefficient, $d$. Colored regions depict exact results, 
		while lines  represent analytical approximations. 
	 \emph{B1:}  Trajectories of sperm-dependent female drive
		 %alleles that can invade the population, 
		 each allele has $s =0.1$ against the
		 homozygotes.  The drive coefficient is denoted by color. 
 }   
\label{Eggsperm}
\end{figure}

@@

\begin{figure}
	\rotatebox{90}{\includegraphics[width = 0.8
          \textwidth]{Figures/Sperm_egg_cartoon_paper_Fig2.eps}}
\caption{Dynamics in 3 allele system
{\bf (A) } The sperm-dependent transmission probabilities of alleles through
female meiosis (female germ cells depicted as circles, sperm indicated by wiggly
tails). In each case the top and bottom entry in each cell give the
transmission probability of the left and right allele in the female
being transmitted to the egg. In the left panel we show the transmission probabilities for
  A, B, and B'. Where B' is a driver allele which is either promotes
  itself through through female meiosis when sperm (a B$^+$ allele,
  $d'>d$) or self-avoiding through the interaction of sperm with female meiosis (a B$^-$ allele,
$d'<d$). In the right panel we depict the transmission probabilities for
  A, B, and A$^-$ allele a non-driven allele that acts to reduce the
  effects of female drive through sperm.
{\bf (B)} Frequency trajectories in the three allele system. }
 \label{Eggsperm_3_allele_cartoon}
\end{figure}

@@

>>>>

\begin{figure}
\includegraphics[width = 1 \textwidth]{Figures/selfprom.eps}
\caption{{\bf{A.}} A visual depiction of our model of `self-promoting' driver. 
	Transmission probabilities for alleles through female
 	 meiosis depend on sperm genotype. 
	 The non-driving $A$-allele, and self-promoting $B$-allele
	 are represented by unfilled and filled circles, respectively. 
	 {\bf{B.}} Evolution of a self-promoter and standard driver. 
	 	Assuming that the fitnesses of drive homozygotes and 
		heterozygotes are $1-s$ and $1$, respectively. 
	 	\emph{Main figure:} Boundary conditions for the invasion 
		and fixation of self-promoting and standard meiotic drivers, 
		with drive coefficient, $d$. Colored regions depict exact results, 
		while lines  represent analytical approximations. 
	 \emph{B1:}  Trajectories of sperm-dependent female drive
		 %alleles that can invade the population, 
		 each allele has $s =0.1$ against the
		 homozygotes.  The drive coefficient is denoted by color. 
 }   
\label{Eggsperm}
\end{figure}

@@

@@

@@

\begin{figure}
	\includegraphics[width = 0.7
          \textwidth]{Figures/twolocus.eps}
\caption{Models of a sperm-acting drive modifier tightly linked to a meiotic driver. 
{\bf (A) } Loci exist in tightly linked haplotypes (top of A). 
	Genotype of sperm at the modifier locus (ancestral and sperm acting modifier empty and filled squares, respectively) alters transmission  
	at the drive locus (circles) during female meiosis. 
	{\bf{A1)}} In the standard model of drive, 
	the driver (filled black circle) and non-driver (empty circle) are transmitted with probabilities $d_0$ 
	and $1-d_0$, respectively. 
	{\bf{A2)}} The $B^+$ haplotype increases the transmission of the drive allele ($d_1 > d_0$), and due to their shared genetic background, also increases its drive. 
	{\bf{A3 \& A4)}} The sperm-acting modifier acts to decrease drive  ($d_1=1/2$ in A3 \& A4. More generally, $d_1 < d_0$). 
		In {\bf{A3}} the drive suppressor exists on the drive background, forming the $B^-$ haplotype. 
		In {\bf{A4}} the drive suppressor exists on the non-drive background, forming the $A^-$ haplotype. 		
{\bf{(B)}} Invasion of a sperm-acting drive suppressor linked to a driver. 
	After the driver ($B$ haplotype) reaches drive selection equilibrium, we introduce a sperm acting drive modifier. 
	We assume full drive ($D_0 =1$), a recessive lethal fitness cost to drive ($h_s=0$, $s=1$) and that the sperm-acting modifier results in a fair meiosis. 
{\bf {B1)}} The $B^-$ allele replaces the ancestral drive haplotype, but segregates at a lower equilibrium frequency.
{\bf {B2)}} The $A^-$ allele replaces the ancestral non-driving haplotype, and in this case, removes the driver from the population. }
 \label{Eggsperm_3_allele_cartoon}
\end{figure}
